Efficiently Handling Guards in the low level design of RPython's tracing JIT

### 2012-07-25 talk/vmil2012/paper.tex
separate related work into two subsections
write about hotspot and escape analysis

@@

>>>>

\subsection{Guards in Other Tracing JITs}
\label{sub:Guards in Other Tracing JITs}

@@

% subsection Guards in Other Tracing JITs (end)

\subsection{Deoptimization in Method-Based JITs}
\label{sub:Deoptimization in Method-Based JITs}

Deoptimization in method-based JITs is used if one of the assumptions
of the code generated by a JIT-compiler changes.
This is often the case when new code is added to the system,
or when the programmer tries to debug the program.

Java Hotspot~\cite{XXX} contains a deoptimization framework that is used
for debugging and when an uncommon trap is triggered.
To be able to do this, Hotspot stores a mapping from optimized states
back to the interpreter state at various deoptimization points.
There is no discussion of the memory use of this information.

The deoptimization information of Hotspot is extended
to support correct behaviour
when scalar replacement of fields is done for non-escaping objects~\cite{XXX}.
The approach is extremely similar to how RPython's JIT handles virtual objects.
For every object that is not allocated in the code,
the deoptimization information contains a description
of the content of the fields.
When deoptimizing code, these objects are reallocated
and their fields filled with the values
described by the deoptimization information.
The paper does not describe any attempts to store this information compactly.

% subsection Deoptimization in Method-Based JITs (end)
